This script creates UVAFME input files for a 1km grid in Canada with sites initialized from Landsat data products.
Write_KLC_files2.R has calculated parameters for initialization; these intermediate outputs just need to be formatted

```{r}
library(data.table)
library(dplyr)
library(tidyverse)
library(terra)

wd = "" # set working directory
inDir = "input_data/KLC/main/"
LandsatDir = "raw/LandsatTreeSpecies/"
tempDir = "scripts/inputs/KLC/intermediate_data/"
```

```{r}
init_sp_i = fread(paste0(tempDir, "landsat_init_sp_test.csv"))
init_dbh_i = fread(paste0(tempDir, "landsat_init_dbh_test.csv"))
```

Build input for GetSiteDat.R
```{r}
sites = init_sp_i[,c("lat","lon")]
soilinput = sites[,1]
soilinput$latitude = sites$lat
soilinput$longitude = sites$lon
soilinput = soilinput[,-1]
soilinput$name = NA
soilinput$site = NA
for(i in 1:nrow(soilinput)) {
  soilinput$name[i] = paste0("site_",i)
  soilinput$site[i] = i
}

colnames(soilinput) = c("latitude","longitude","name","site")
write.csv(soilinput, paste0(tempDir, "Landsat_init_sitedat_input.csv"), quote = F, row.names = F)
```

Run GetSoilDat.R

Write inputs: site, sitelist, rangelist.
```{r}
soil = read.csv(paste0(tempDir, "Landsat_init_soildat_output.csv"))

soil$A_depth = 1
soil$flow = 0; soil$row = 0; soil$col = 0; soil$ind = 0

site = soil %>% dplyr::select(site,latitude,longitude,name,region,elevation,slope,aspect,a_sat,a_fc,a_pwp,o_sat,o_fc,o_pwp,a_bd,o_bd,itxt,hum_init,A_depth,wprob,flow,row,col,ind)

# Adding the rest of the columns
site$management = 0
site$sel_cutting = 0
site$planting = "PICEglau" # only thing that gets planted (planting only called after harvest)
site$viability = 1
site$rotation_time = 0
site$dbh_thresh = 0
site$thinning = 0
site$year_management = 0
site$thin_perc = 0
site$shearblading = 0
site$pruning = 0
site$init_year = 2015

site$unit = 0

site = site %>% dplyr::select(site,latitude,longitude,name,region,elevation,slope,aspect,a_sat,a_fc,a_pwp,o_sat,o_fc,o_pwp,a_bd,o_bd,itxt,hum_init,A_depth,wprob,flow,row,col,ind,management,sel_cutting,planting,viability,rotation_time,dbh_thresh,thinning,year_management,thin_perc,shearblading,pruning,unit,init_year)

site = na.omit(site)

# Adjusting drainage based on forest type
site = merge(site, init_sp_i, by.x = c("site","latitude","longitude"), by.y = c("siteID","lat","lon"))

site[site$PICEmari > 0.4,]$hum_init = 200
site[site$PICEmari > 0.4,]$a_sat = max(site[site$PICEmari > 0.4,]$a_sat, 0.45)
site[site$PICEmari > 0.4,]$o_sat = max(site[site$PICEmari > 0.4,]$o_sat, 0.45)
site[site$PICEmari > 0.4,]$a_fc = max(site[site$PICEmari > 0.4,]$a_fc, 0.3)
site[site$PICEmari > 0.4,]$o_fc = max(site[site$PICEmari > 0.4,]$o_fc, 0.3)

site[site$PICEmari <= 0.4,]$a_sat = min(site[site$PICEmari <= 0.4,]$a_sat, 0.35)
site[site$PICEmari <= 0.4,]$o_sat = min(site[site$PICEmari <= 0.4,]$o_sat, 0.35)
site[site$PICEmari <= 0.4,]$a_fc = min(site[site$PICEmari <= 0.4,]$a_fc, 0.2)
site[site$PICEmari <= 0.4,]$o_fc = min(site[site$PICEmari <= 0.4,]$o_fc, 0.2)
site[site$PICEmari <= 0.4,]$a_pwp = min(site[site$PICEmari <= 0.4,]$a_pwp, 0.06)
site[site$PICEmari <= 0.4,]$o_pwp = min(site[site$PICEmari <= 0.4,]$o_pwp, 0.06)


site = site %>% dplyr::select(site,latitude,longitude,name,region,elevation,slope,aspect,a_sat,a_fc,a_pwp,o_sat,o_fc,o_pwp,a_bd,o_bd,itxt,hum_init,A_depth,wprob,flow,row,col,ind,management,sel_cutting,planting,viability,rotation_time,dbh_thresh,thinning,year_management,thin_perc,shearblading,pruning,unit,init_year)


# Adjusting sites with contradictory drainage params
site[xor(site$a_sat<site$a_fc, site$a_fc<site$a_pwp),]
nrow(site[xor(site$o_sat<site$o_fc, site$o_fc<site$o_pwp),]) # this has some problem sites
nrow(site[site$o_sat<site$o_pwp,]) 
nrow(site[site$o_fc<site$o_pwp,]) 


temp = site[site$o_sat<site$o_pwp,]
for(i in 1:nrow(temp)) {
  temp[i,"o_sat"] = temp[i, "o_pwp"] + 0.02
}
site[site$o_sat<site$o_pwp,] = temp


temp = site[site$o_fc<site$o_pwp,]
for(i in 1:nrow(temp)) {
  temp[i,"o_fc"] = round(temp[i,"o_pwp"] + (temp[i,"o_sat"] - temp[i,"o_pwp"])/2,2)
}
site[site$o_fc<site$o_pwp,] = temp


# Read in stand age; initiate prescribed burns in sites with recent disturbances 
age = rast(paste0(LandsatDir, "forestage_2019/CA_forest_age_2019.tif"))  #years
oldcrs = crs(age)
wgs84   = "+proj=longlat +datum=WGS84"
tile = ext(-128,-127,59,60) #WGS84 coords
tempext = ext(-1.85e6, -1.65e6,1.5e6, 1.8e6) # Preliminary crop to make projection faster

# Domspec = rast(paste0(LandsatDir, "lead_species_2019/CA_forest_lead_tree_species.tif"))
# Domspec = crop(Domspec, tempext)

# r = rast(ext(Domspec), res = 1000, crs = oldcrs)
age = terra::crop(age, tempext)

nad83 = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs +type=crs"
tile2 = terra::project(tile, from = wgs84, to =nad83)
r = rast(ext = tile2, res = 1000, crs = nad83)

# age[age == 0,] <- NA
age = terra::project(age, nad83, method = "near")
agemean = terra::resample(age, r)

agemean = project(agemean, wgs84, method = "near")
agemean = as.points(agemean)
agemean = as.data.frame(agemean, geom = "XY")
colnames(agemean) = c("age","x","y")
agemean$x = round(agemean$x, 4)
agemean$y = round(agemean$y, 4)

min(agemean$age) # if below 4, some sites need prescribed fires

site$prescribed_burn = 0
site = merge(site, agemean, by.x = c("latitude","longitude"), by.y = c("y","x"))

site[site$age <=4,]$prescribed_burn = 1
site[site$age <= 4,]$year_management = 2015
site[site$age <= 3,]$year_management = 2016
site[site$age <= 2,]$year_management = 2017
site[site$age <= 1,]$year_management = 2018

site = site %>% dplyr::select(site,latitude,longitude,name,region,elevation,slope,aspect,a_sat,a_fc,a_pwp,o_sat,o_fc,o_pwp,a_bd,o_bd,itxt,hum_init,A_depth,wprob,flow,row,col,ind,management,sel_cutting,planting,viability,rotation_time,dbh_thresh,thinning,year_management,thin_perc,shearblading,pruning,unit,init_year, prescribed_burn)

#actually, none of the sites are young enough for a prescribed burn
site = site %>% dplyr::select(site,latitude,longitude,name,region,elevation,slope,aspect,a_sat,a_fc,a_pwp,o_sat,o_fc,o_pwp,a_bd,o_bd,itxt,hum_init,A_depth,wprob,flow,row,col,ind,management,sel_cutting,planting,viability,rotation_time,dbh_thresh,thinning,year_management,thin_perc,shearblading,pruning,unit,init_year)

write.csv(site, paste0(inDir, "UVAFME2018_site.csv"), row.names = F, quote = F)

sitelist = cbind(site$site, 1:nrow(site))
colnames(sitelist) = c("siteID","runID")
sitelist = as.data.frame(sitelist)
sitelist$altitude = NA; sitelist$end = NA
write.csv(sitelist, paste0(inDir, "UVAFME2018_sitelist.csv"), quote = F, row.names = F, na = "")

rangelist  = site %>% dplyr::select(site, latitude, longitude)
rangelist$ALNUsinu = 1
rangelist$ALNUtenu = 1
rangelist$BETUneoa = 1
rangelist$LARIlari = 0
rangelist$PICEglau = 1
rangelist$PICEmari = 1
rangelist$POPUbals = 1
rangelist$POPUtrem = 1
rangelist$SALIplan = 0
rangelist$SALIscou = 1
rangelist$PINUcont = 1
# rangelist$PICEenge = 1 # not in init files... if it's here it causes problems
rangelist$ABIElasi = 1

write.csv(rangelist, paste0(inDir, "UVAFME2018_rangelist.csv"), quote = F, row.names = F)

```

Copy inputs: specieslist, litterpars. Verify that CA species are included. 

Write inputs: initialization files 
```{r}
init_sp = init_sp_i
init_sp$ALNUtenu = 0
init_sp$ALNUsinu = 0
init_sp$SALIscou = 0
init_sp$SALIplan = 0
init_sp$LARIlari = 0
init_sp$BETUneoa = 0
init_sp$POPUbals = 0

init_sp$site = init_sp$siteID
init_sp$totstems = -999
# Order of species doesn't matter
init_sp = init_sp %>% dplyr::select(site,totstems,BA,ALNUsinu,ALNUtenu,BETUneoa,LARIlari,
                             PICEglau,PICEmari,POPUbals,POPUtrem,SALIplan,SALIscou,PINUcont,ABIElasi)

fwrite(init_sp, paste0(inDir, "UVAFME2018_init_spec.csv"))

init_dbh = init_dbh_i
init_dbh$site = init_dbh$siteID
x = ncol(init_dbh)
cats = c("less5","5to10","10to20","20to30","30to40","40to50","50to60","60to70","70to80","80up")
newspec = c("ALNUsinu","ALNUtenu","BETUneoa","LARIlari","POPUbals","SALIplan","SALIscou")

newspec = c(newspec, "ABIElasi")

for(i in 1:length(newspec)) {
  for(j in 1:length(cats)) {
    name = (paste0(newspec[i],"_",cats[j]))
    init_dbh = init_dbh %>% add_column(tempcol = 0)
    colnames(init_dbh)[x+10*(i-1)+j] = name
  }
}

specorder = c("ALNUsinu","ALNUtenu","BETUneoa","LARIlari",
                             "PICEglau","PICEmari","POPUbals","POPUtrem","SALIplan","SALIscou","PINUcont","ABIElasi")
init_dbh = init_dbh %>% dplyr::select(site, paste0(specorder[1], "_", cats),paste0(specorder[2], "_", cats),paste0(specorder[3], "_", cats),
                               paste0(specorder[4], "_", cats),paste0(specorder[5], "_", cats),paste0(specorder[6], "_", cats),
                               paste0(specorder[7], "_", cats),paste0(specorder[8], "_", cats),paste0(specorder[9], "_", cats),
                               paste0(specorder[10], "_", cats),paste0(specorder[11], "_", cats),paste0(specorder[12], "_", cats))
fwrite(init_dbh, paste0(inDir, "UVAFME2018_init_dbh.csv"))

```

Make input file for climateNA (v7.31). Output csv may need to be opened in excel and re-saved so EOF works for climateNA software
```{r}
site = fread(paste0(inDir, "UVAFME2018_site.csv"))
climateNAinput = site %>% dplyr::select(site, name, latitude, longitude, elevation)
colnames(climateNAinput) = c("ID1","ID2","lat","long","el")

write.csv(climateNAinput, paste0(tempDir, "Landsat_init_CNA_input.csv"), row.names = F, quote = F)
```


Run 002_param_sites.R to create 5 files; 4 for normal climate, 1 for lightning. Make sure input directories/ files are current. Files from this script are already present in proper directory; raw data to create them isn't available 

Make up lightning inputs; 002_param_sites calls on data from Alaska which doesn't have enough strikes in BC
Params here based on average monthly lightning ground strikes were estimated from summary CLDN statistics for north/ interior British Columbia from 1999-2018.
```{r}
sites = fread(paste0(inDir, "UVAFME2018_site.csv"))

jun = 480
jul = 900
aug = 580
sep = 140
prp = c(0,0,0,0,0,jun,jul,aug,sep,0,0,0)
prp = prp/sum(prp) #monthly proportions for annual lightning strikes

strikes = 0.1/4 #annual ground strikes per 1km2 in Northern BC

lightning = sites %>% dplyr::select(site, latitude, longitude)
lightning$strmn_jan = 0;
lightning$strmn_feb = 0;
lightning$strmn_mar = 0;
lightning$strmn_apr = 0;
lightning$strmn_may = 0;
lightning$strmn_jun = strikes*prp[6]
lightning$strmn_jul = strikes*prp[7]
lightning$strmn_aug = strikes*prp[8]
lightning$strmn_sep = strikes*prp[9]
lightning$strmn_oct = 0;
lightning$strmn_nov = 0;
lightning$strmn_dec = 0;


lightning$strsd_jan = 0;
lightning$strsd_feb = 0;
lightning$strsd_mar = 0;
lightning$strsd_apr = 0;
lightning$strsd_may = 0;
lightning$strsd_jun = 0;
lightning$strsd_jul = 0;
lightning$strsd_aug = 0;
lightning$strsd_sep = 0;
lightning$strsd_oct = 0;
lightning$strsd_nov = 0;
lightning$strsd_dec = 0;

fwrite(lightning, paste0(inDir, "UVAFME2018_lightning.csv"))
```

Make climate GCM and lightning GCM inputs. Data from ClimateNA v7.31
```{r}
cNAobs = fread(paste0(tempDir,"Landsat_init_CNA_2015-2021MP.csv"))

cNAout = fread(paste0(tempDir, "Landsat_init_CNA_8GCMs_ensemble_ssp245_2022-2100MP.csv"))
sites = fread(paste0(inDir, "UVAFME2018_site.csv"))

cNAout = rbind(cNAobs, cNAout)

cNAout = select(cNAout, contains(c("Year","ID1","Tmin","Tmax","PPT")))
cNAout = merge(sites[,c("site","latitude","longitude")], cNAout, by.x = "site", by.y = "ID1")
cols = c("site" ,"latitude" ,"longitude"  ,"year" ,"tmin_jan" ,"tmin_feb" ,"tmin_mar" ,"tmin_apr" ,"tmin_may" ,"tmin_jun" ,"tmin_jul" ,'tmin_aug' ,"tmin_sep" ,"tmin_oct" ,"tmin_nov" ,"tmin_dec" ,"tmax_jan" ,"tmax_feb" ,"tmax_mar" ,"tmax_apr" ,"tmax_may" ,"tmax_jun" ,"tmax_jul" ,"tmax_aug" ,"tmax_sep" ,"tmax_oct" ,"tmax_nov" ,"tmax_dec" ,"prcp_jan" ,"prcp_feb" ,"prcp_mar" ,"prcp_apr" ,"prcp_may" ,"prcp_jun" ,"prcp_jul" ,"prcp_aug" ,"prcp_sep" ,"prcp_oct" ,"prcp_nov" ,"prcp_dec")
colnames(cNAout) = cols

cNAout = cNAout[order(cNAout$site, cNAout$year),]

fwrite(cNAout, paste0(inDir, "UVAFME2018_climate_GCM_8Ensemble_SSP245.csv"))

obs = cNAout[cNAout$year<2022,] #2015-2021 observations; copy over for GCM 85

cNAout = fread(paste0(tempDir, "Landsat_init_CNA_8GCMs_ensemble_ssp585_2022-2100MP.csv"))

cNAout = select(cNAout, contains(c("Year","ID1","Tmin","Tmax","PPT")))
cNAout = merge(sites[,c("site","latitude","longitude")], cNAout, by.x = "site", by.y = "ID1")
cols = c("site" ,"latitude" ,"longitude"  ,"year" ,"tmin_jan" ,"tmin_feb" ,"tmin_mar" ,"tmin_apr" ,"tmin_may" ,"tmin_jun" ,"tmin_jul" ,'tmin_aug' ,"tmin_sep" ,"tmin_oct" ,"tmin_nov" ,"tmin_dec" ,"tmax_jan" ,"tmax_feb" ,"tmax_mar" ,"tmax_apr" ,"tmax_may" ,"tmax_jun" ,"tmax_jul" ,"tmax_aug" ,"tmax_sep" ,"tmax_oct" ,"tmax_nov" ,"tmax_dec" ,"prcp_jan" ,"prcp_feb" ,"prcp_mar" ,"prcp_apr" ,"prcp_may" ,"prcp_jun" ,"prcp_jul" ,"prcp_aug" ,"prcp_sep" ,"prcp_oct" ,"prcp_nov" ,"prcp_dec")
colnames(cNAout) = cols

cNAout = rbind(cNAout, obs)

cNAout = cNAout[order(cNAout$site, cNAout$year),]
cNAout = cNAout[cNAout$site %in% sites$site,]
fwrite(cNAout, paste0(inDir, "UVAFME2018_climate_GCM_8Ensemble_SSP585.csv"))


# Creating lightning GCM data 
histclim = fread(paste0(inDir, "UVAFME2018_climate.csv"))
GCM45 = fread(paste0(inDir, "UVAFME2018_climate_GCM_8Ensemble_SSP245.csv"))
GCM85 = fread(paste0(inDir, "input_data/KLC/UVAFME2018_climate_GCM_8Ensemble_SSP585.csv"))
lightning = fread(paste0(inDir, "UVAFME2018_lightning.csv"))

histclim = histclim %>% group_by(site) %>% mutate(tave_jan = (tmin_jan+tmax_jan)/2,
                                                  tave_feb = (tmin_feb+tmax_feb)/2,
                                                  tave_mar = (tmin_mar+tmax_mar)/2,
                                                  tave_apr = (tmin_apr+tmax_apr)/2,
                                                  tave_may = (tmin_may+tmax_may)/2,
                                                  tave_jun = (tmin_jun+tmax_jun)/2,
                                                  tave_jul = (tmin_jul+tmax_jul)/2,
                                                  tave_aug = (tmin_aug+tmax_aug)/2,
                                                  tave_sep = (tmin_sep+tmax_sep)/2,
                                                  tave_oct = (tmin_oct+tmax_oct)/2,
                                                  tave_nov = (tmin_nov+tmax_nov)/2,
                                                  tave_dec = (tmin_dec+tmax_dec)/2)

GCM45 = GCM45 %>% group_by(site, year) %>% mutate(tave_jan = (tmin_jan+tmax_jan)/2,
                                                  tave_feb = (tmin_feb+tmax_feb)/2,
                                                  tave_mar = (tmin_mar+tmax_mar)/2,
                                                  tave_apr = (tmin_apr+tmax_apr)/2,
                                                  tave_may = (tmin_may+tmax_may)/2,
                                                  tave_jun = (tmin_jun+tmax_jun)/2,
                                                  tave_jul = (tmin_jul+tmax_jul)/2,
                                                  tave_aug = (tmin_aug+tmax_aug)/2,
                                                  tave_sep = (tmin_sep+tmax_sep)/2,
                                                  tave_oct = (tmin_oct+tmax_oct)/2,
                                                  tave_nov = (tmin_nov+tmax_nov)/2,
                                                  tave_dec = (tmin_dec+tmax_dec)/2)

GCM85 = GCM85 %>% group_by(site, year) %>% mutate(tave_jan = (tmin_jan+tmax_jan)/2,
                                                  tave_feb = (tmin_feb+tmax_feb)/2,
                                                  tave_mar = (tmin_mar+tmax_mar)/2,
                                                  tave_apr = (tmin_apr+tmax_apr)/2,
                                                  tave_may = (tmin_may+tmax_may)/2,
                                                  tave_jun = (tmin_jun+tmax_jun)/2,
                                                  tave_jul = (tmin_jul+tmax_jul)/2,
                                                  tave_aug = (tmin_aug+tmax_aug)/2,
                                                  tave_sep = (tmin_sep+tmax_sep)/2,
                                                  tave_oct = (tmin_oct+tmax_oct)/2,
                                                  tave_nov = (tmin_nov+tmax_nov)/2,
                                                  tave_dec = (tmin_dec+tmax_dec)/2)


#Methods from Foster et al 2022:
# Change in lightning strike frequency was forced according to predictions in
# Veraverbeke et al. (2017). Veraverbeke et al. (2017) predicted a 24% and 59%
# increase in lightning strike frequency for the Northwest Territories and interior
# Alaska, respectively during a 2.84ºC and 2.85ºC increase in temperature, respectively. We thus scaled lightning strike frequency by 20.7% (59/2.85) for each
# degree C increase for interior Alaska and by 8.45% (24/2.84) for each degree C
# increase in the Northwest Territories.

histclim = histclim[order(histclim$site),]
GCM45 = GCM45[order(GCM45$site, GCM45$year),]
GCM85 = GCM85[order(GCM85$site, GCM85$year),]

lightningGCM45 = data.frame(matrix(ncol=16 ,nrow=0, dimnames=list(NULL, c(colnames(lightning)[1:3], "year", colnames(lightning)[4:15]))))
lightningGCM85 = data.frame(matrix(ncol=16 ,nrow=0, dimnames=list(NULL, c(colnames(lightning)[1:3], "year", colnames(lightning)[4:15]))))

for(y in 2015:2018) {
  lightningGCM45 = rbind(lightningGCM45, cbind(lightning[,1:3], rep(y, nrow(lightning)), lightning[,4:15]))
  lightningGCM85 = rbind(lightningGCM85, cbind(lightning[,1:3], rep(y, nrow(lightning)), lightning[,4:15]))
}

for (y in 2019:2100) {
  tempdiff = GCM45[GCM45$year == y,41:52] - histclim[,40:51]
  lGCM45 = mapply(`*`, 1+(0.23*tempdiff), lightning[,4:15])
  colnames(lightningGCM45)[5:16] = colnames(lGCM45)
  lightningGCM45 = rbind(lightningGCM45, cbind(lightning[,1:3], rep(y, nrow(lightning)), lGCM45))
  
  tempdiff = GCM85[GCM85$year == y,41:52] - histclim[,40:51]
  lGCM85 = mapply(`*`, 1+(0.23*tempdiff), lightning[,4:15])
  colnames(lightningGCM85)[5:16] = colnames(lGCM85)
  lightningGCM85 = rbind(lightningGCM85, cbind(lightning[,1:3], rep(y, nrow(lightning)), lGCM85))
}

colnames(lightningGCM45) =c(colnames(lightning)[1:3], "year", colnames(lightning)[4:15])
colnames(lightningGCM85) =c(colnames(lightning)[1:3], "year", colnames(lightning)[4:15])

fwrite(lightningGCM45, paste0(inDir, "UVAFME2018_lightning_GCM_SSP245.csv"))
fwrite(lightningGCM85, paste0(inDir, "UVAFME2018_lightning_GCM_SSP585.csv"))

```
Copy specieslist and litterpars into main inputs


Create runtime and filelists (just edit txt) and output directories

Create and organize I/O folders for multiple runs and filelists
```{r}
dir.create(file.path('input_data/KLC/gcm45'), showWarnings = FALSE)
dir.create(file.path('input_data/KLC/gcm85'), showWarnings = FALSE)
dir.create(file.path('input_data/KLC/rtdir'), showWarnings = FALSE)
dir.create(file.path('input_data/KLC/rtdir/hist'), showWarnings = FALSE)
dir.create(file.path('input_data/KLC/rtdir/cc'), showWarnings = FALSE)
rt = readLines(paste0(testdir, "UVAFME2018_runtime.txt"))
rt #review this
writeLines(rt, "input_data/KLC/rtdir/cc/UVAFME2018_runtime.txt")
rt[24] = "with_clim_change = .false."
rt[25] = "use_gcm=.false."
writeLines(rt, "input_data/KLC/rtdir/hist/UVAFME2018_runtime.txt")

dir.create(file.path('file_lists/KLC'), showWarnings = FALSE)

# Divide into 10 groups for gcm scenarios
groups = 20

clims = c("hist","gcm45","gcm85")
slist = fread(paste0(maindir, "UVAFME2018_sitelist.csv"))
clim45 = fread("input_data/KLC/gcm45/UVAFME2018_climate_GCM.csv")
lightning45 = fread("input_data/KLC/gcm45/UVAFME2018_lightning_GCM.csv")
clim85 = fread("input_data/KLC/gcm85/UVAFME2018_climate_GCM.csv")
lightning85 = fread("input_data/KLC/gcm85/UVAFME2018_lightning_GCM.csv")

set.seed(147)
slist$group = ceiling(runif(nrow(slist), 0, groups))
for(i in 1:groups) {
  dir.create(file.path(paste0('input_data/KLC/gcm45/',i,"/")), showWarnings = FALSE)
  dir.create(file.path(paste0('input_data/KLC/gcm85/',i,"/")), showWarnings = FALSE)
  
  sites = slist[slist$group == i,]$site
  slist.sub = slist[slist$site %in% sites,1:4]
  clim45.sub = clim45[clim45$site %in% sites,]
  clim85.sub = clim85[clim85$site %in% sites,]
  lightning45.sub = lightning45[lightning45$site %in% sites,]
  lightning85.sub = lightning85[lightning85$site %in% sites,]
  
  fwrite(slist.sub, paste0('input_data/KLC/gcm45/',i,"/UVAFME2018_sitelist.csv"))
  fwrite(slist.sub, paste0('input_data/KLC/gcm85/',i,"/UVAFME2018_sitelist.csv"))
  fwrite(clim45.sub, paste0('input_data/KLC/gcm45/',i,"/UVAFME2018_climate_GCM.csv"))
  fwrite(clim85.sub, paste0('input_data/KLC/gcm85/',i,"/UVAFME2018_climate_GCM.csv"))
  fwrite(lightning45.sub, paste0('input_data/KLC/gcm45/',i,"/UVAFME2018_lightning_GCM.csv"))
  fwrite(lightning85.sub, paste0('input_data/KLC/gcm85/',i,"/UVAFME2018_lightning_GCM.csv"))
}

clims2 = c("hist","cc","cc")

# Filelists
l1 = "&filenames"
l2 = "input_directory='input_data/KLC/main/'"
l3 = "output_directory='output_data/KLC/" # clim/group*
l4 = "climate_directory='input_data/KLC/main/'"
l5 = "site_directory='input_data/KLC/main/'"
l6 = "sitelist_directory='input_data/KLC/" #clim/group*
l7 = "GCM_directory='input_data/KLC/" #clim/group*
l8 = "rt_directory='input_data/KLC/rtdir/" #clim
l9 = "speclist_directory='input_data/KLC/main/'"
l10 = "/"


for(i in 1) {
  l3a = paste0(l3, clims[i], "/'")
  l6a = paste0(l6, "main/'")
  l7a = paste0(l7, "'")
  l8a = paste0(l8, clims2[i], "/'")
  flist = c(l1, l2, l3a, l4, l5, l6a, l7a, l8a, l9, l10)
  writeLines(flist, paste0("file_lists/KLC/file_list_", clims[i], ".txt"))
}

for(i in 2:3) {
  for(j in 1:groups) {
    l3a = paste0(l3, clims[i], "/", j, "/'")
    l6a = paste0(l6, clims[i], "/", j, "/'")
    l7a = paste0(l7, clims[i], "/", j, "/'")
    l8a = paste0(l8, clims2[i], "/'")
    flist = c(l1, l2, l3a, l4, l5, l6a, l7a, l8a, l9, l10)
    writeLines(flist, paste0("file_lists/KLC/file_list_", clims[i],"_",j, ".txt"))
  }
}

dir.create(file.path('output_data/KLC/hist'), showWarnings = FALSE)
dir.create(file.path('output_data/KLC/gcm45'), showWarnings = FALSE)
dir.create(file.path('output_data/KLC/gcm85'), showWarnings = FALSE)

for(i in 1:groups) {
  dir.create(file.path(paste0('output_data/KLC/gcm45/',i,"/")), showWarnings = FALSE)
  dir.create(file.path(paste0('output_data/KLC/gcm85/',i,"/")), showWarnings = FALSE)
}

# create jobs
dir.create(file.path("logs/CA_landsat/"))
jobdir = "jobfiles/CA_landsat/"
l1 = "#!/bin/bash"
# l2 = "#SBATCH -o logs/CA_landsat/hist.log"
# l3 = "#SBATCH -o logs/CA_landsat/hist.err.log"
l4 = paste0("#SBATCH --chdir=", wd)
l5 = "#SBATCH --mail-type=ALL"
l6 = "#SBATCH --mem=3000"
l7 = "#SBATCH --time=2:00:00"
# l8 = "name=file_lists/KLC/file_list_hist.txt"
l9 = "srun UVAFME_init $name"

joblist = "sbatch jobfiles/CA_landsat/hist.slurm"
for(i in 2:3) {
  for(j in 1:groups) {
    name = paste0(clims[i], "_", j)
    l2a = paste0("#SBATCH -o logs/CA_landsat/",clims[i],"_",j,".log")
    l3a = paste0("#SBATCH -o logs/CA_landsat/",clims[i],"_",j,".err.log")
    l8a = paste0("name=file_lists/KLC/file_list_", clims[i],"_",j, ".txt")
    lines = c(l1, l2a, l3a, l4, l5, l6, l7, l8a, l9)
    
    jobfile = paste0(jobdir, name, ".slurm")
    fileConn <- file(jobfile)
    writeLines(lines, fileConn)
    close(fileConn)
    joblist = c(joblist, paste0("sbatch ",jobfile))
  }
}

writeLines(joblist, paste0(jobdir, "joblist.txt"))

```

to test one script... 
cd to working directory
./UVAFME_init file_lists/KLC/file_list_hist.txt