---
title: "TVSF_2km_inputs"
author: "Shelby Sundquist"
date: "2022-12-06"
output: html_document
---

### Updated Feb, 2023 for climate 8-model ensemble projections and use on monsoon


Tanana Valley site parameterization
-Script must be run interactively; requires intermediate upload, scripts, and download from Monsoon

Load libraries, set directories
```{r}
library(terra)
library(data.table)
library(dplyr)
library(raster)
library(rgdal)

dataDir = "raw/"
tempDir = "scripts/inputs/TVSF/intermediate_data/"
outDir = "TVSF/clims_testing/main/"
```


Input block
Shapefile with Alaska SF unit boundaries downloaded from:  https://forestrymaps-soa-dnr.hub.arcgis.com/datasets/SOA-DNR::state-forest-boundary-public-view/explore?location=59.970122%2C-147.760600%2C5.33
on 12-6-2022
With inventory boundaries downloaded from: https://forestrymaps-soa-dnr.hub.arcgis.com/apps/alaska-statewide-forest-inventory/explore on 4-27-2022
```{r}
units = vect(paste0(dataDir,"State_Forest_Boundary_Public_View/State_Forest_Boundary.shp"))
units = units[units$descriptio == "Tanana Valley State Forest",]
units = units[!is.na(units$unit),]
plot(units) #check
inv = vect(paste0(dataDir,"Tanana_Valley_Forest_Inventory_with_Tables_Public_View-shp/TV_Timber_Types.shp"))
inv$Year = as.integer(inv$Date_Typed) # This line did not work and I have no idea why good grief!
```

Combining and rasterizing shapefiles to produce 500x500m site centroids for UVAFME
```{r}
#Rasterize units
res = 500 #500m grid
r = rast(units, resolution = res) 
locs = terra::rasterize(units, r, field = "unit")
newcrs = "+proj=longlat +datum=WGS84"
locs = project(locs, newcrs)

#Get %area per strata in each pixel
#Rasterize decides cell value by the polygon in the center of the cell
r = rast(inv, resolution = res/10) #100 inventory cells to sample per UVAFME site
invr = terra::rasterize(inv, r, field = "STRATUM")
invr = project(invr, newcrs)
invr = crop(invr, ext(locs))
invr = resample(invr, locs, method = "mode")
# invr$STRATUM = as.factor(invr$STRATUM)

#Getting inventory dates
invr2 = terra::rasterize(inv, r, field = "Year")
invr2 = project(invr2, newcrs)
invr2 = crop(invr2, ext(locs))
invr2 = resample(invr2, locs, method = "mode")

#Getting management area for initialization (Tok is less productive)
mgmt = terra::rasterize(inv, r, field = "UNIT")
mgmt = project(mgmt, newcrs)
mgmt = resample(mgmt, locs, method = "mode")


locs = as.points(locs)
invr = as.points(invr)
invr2 = as.points(invr2)
mgmt = as.points(mgmt)
terra::plot(x = locs, "unit")
terra::plot(x = invr, "STRATUM")
terra::plot(invr2, "Year")
terra::plot(mgmt, "UNIT")
dflocs = as.data.frame(locs, geom = "XY")
dfinv = as.data.frame(invr, geom = "XY")
dfinv2 = as.data.frame(invr2, geom = "XY")
dfmgmt = as.data.frame(mgmt, geom = "XY")

# rm(units)
# rm(inv)

dflocs = merge(dflocs, dfinv, by = c("x","y"))
dflocs = merge(dflocs, dfinv2, by = c("x","y"))
dflocs = merge(dflocs, dfmgmt, by = c("x","y"))

write.csv(dflocs, paste0(tempDir, "unit_stratum_date_locs.csv"), quote = F, row.names = F)
```

Building input file for GetSiteDat.R 
```{r}
soilinput = dflocs[,1:2]
soilinput$name = NA
soilinput$site = NA
for(i in 1:nrow(soilinput)) {
  soilinput$name[i] = paste0("tvsf_",i)
  soilinput$site[i] = i
}

colnames(soilinput) = c("longitude","latitude","name","site")
write.csv(soilinput, paste0(tempDir, "sitedat_input.csv"), quote = F, row.names = F)
```
Run GetSiteDat.R; Not all the data for this script is in raw, but the output from running this script is in intermediate data, allowing you to skip this step

Building site.csv with soil data from Monsoon script
(From init::Input.f90 2-20-2023) file variables are:
                sitename, siteregion, elevation, slope, aspect, asat, afc,     &
                apwp, osat, ofc, opwp, abd, obd, itxt, hum_input,              &
                A_depth, wprob, flow, row, col, ind,      &
                management, sel_cutting, planting, viability, rotation_time,   &
                dbh_thresh, thinning, year_management, thin_perc, shearblading, &
                pruning, unit, init_year 

```{r}
soil = read.csv(paste0(tempDir, "soildat_output.csv"))
dflocs = read.csv(paste0(tempDir,"unit_stratum_date_locs.csv"))
key = read.csv(paste0(tempDir, "stratum_key.csv"))

dflocs$Date_Typed = dflocs$Year
soil$A_depth = 1
soil$flow = 0; soil$row = 0; soil$col = 0; soil$ind = 0
soil = merge(soil, dflocs, by.x = c("longitude","latitude"), by.y = c("x","y"))

site = soil %>% select(site,latitude,longitude,name,region,elevation,slope,aspect,a_sat,a_fc,a_pwp,o_sat,o_fc,o_pwp,a_bd,o_bd,itxt,hum_init,A_depth,wprob,flow,row,col,ind, unit, STRATUM, Date_Typed)

#checking and fixing soil issues
summary(site[,9:17])
temp = site[is.na(site$itxt),]
summary(as.factor(temp$STRATUM)) 
# these are nearly all river/ lake/ bare ground sites that fell within units. I'm pretty comfortable all of discarding these
site = site[!is.na(site$itxt),]

# site[xor(site$a_sat<site$a_fc, site$a_fc<site$a_pwp),]
# site[xor(site$o_sat<site$o_fc, site$o_fc<site$o_pwp),] # this has some problem sites
# site[site$o_sat<site$o_pwp,]

temp = site[site$o_fc<site$o_pwp,]
for(i in 1:nrow(temp)) {
  temp[i,"o_fc"] = round(temp[i,"o_pwp"] + (temp[i,"o_sat"] - temp[i,"o_pwp"])/2,2)
}
site[site$o_fc<site$o_pwp,] = temp

summary(as.factor(site$STRATUM))
key[,2:3]
# less than 20 is forest. Higher numbers are shrubs, meadow, water, other non-forest

site = site[site$STRATUM <= 20,]


# Adding the rest of the columns
site$management = 0
site$sel_cutting = 0
site$planting = "PICEglau" # only thing that gets planted (planting only called after harvest)
site$viability = 1
site$rotation_time = 0
site$dbh_thresh = 0 
site$thinning = 0
site$year_management = 0
site$thin_perc = 0
site$shearblading = 0
site$pruning = 0
site$init_year = site$Date_Typed

site = site %>% select(site,latitude,longitude,name,region,elevation,slope,aspect,a_sat,a_fc,a_pwp,o_sat,o_fc,o_pwp,a_bd,o_bd,itxt,hum_init,A_depth,wprob,flow,row,col,ind,management,sel_cutting,planting,viability,rotation_time,dbh_thresh,thinning,year_management,thin_perc,shearblading,pruning,unit,init_year)

write.csv(site, paste0(outDir, "UVAFME2018_site.csv"), row.names = F, quote = F)
```


Building input file for climateNA
```{r}
climateNAinput = site %>% select(site, name, latitude, longitude, elevation)
colnames(climateNAinput) = c("id1","id2","lat","long","elev")

climateNAinput_1983 = site[site$init_year == 1983,] %>% select(site, name, latitude, longitude, elevation)
colnames(climateNAinput_1983) = c("id1","id2","lat","long","elev")

climateNAinput_2013 = site[site$init_year == 2013,] %>% select(site, name, latitude, longitude, elevation)
colnames(climateNAinput_2013) = c("id1","id2","lat","long","elev")


write.csv(climateNAinput, paste0(tempDir, "climateNAinput.csv"), quote = F, row.names = F)
write.csv(climateNAinput_1983, paste0(tempDir, "climateNAinput_1983.csv"), quote = F, row.names = F)
write.csv(climateNAinput_2013, paste0(tempDir, "climateNAinput_2013.csv"), quote = F, row.names = F)
```

ClimateNA_v7.31 program (2022)
Historical time series 1983/2013-2021 - monthly variables (input = climateNAinput_xxxx.csv) - primary variables
Future time series 2022-2100 - monthly variables - 8 model ensemble SSP 2-4.5 and SSP 5-8.5 (input = climateNAinput.csv) - primary variables
Historical time series 1961-1990 all variables all sites (input = climateNAinput.csv)

Note: climateNA731 requires eof from excel; open csvs in excel and re-save for them to work


Build climate files (4):
ClimateNA - Historical Time Series 1961-1990 - Monthly variables (input = climNAinput.csv)
Also - 


Calling ClimateNA from R
```{r}
# cNADir = "Parameterization/ClimateNA_v731/"
# exe = "ClimateNA_v7.31.exe"
# 
# # Historical time series (x2)
# input = paste0(Dir, tempDir, "ClimateNAinput_2013.csv")
# output= paste0(Dir, tempDir, "ClimateNAoutput_2013_2013-2021MP.csv")
# call = "/Year_2013.ann"
# system2(paste0(cNADir, exe), args = c("/M", call, input, output), wait = T)

# This isn't working, even following the instructions in the help doc. You have to run it in the program itself (or go back to the intermediate data folder and skip this step)
```

Run 002_Param_Sites.R to create 5 files; 4 for normal climate, 1 for lightning
Again, not all these data are in raw, but the outputs from this script already exist in input_data

Building climateGCM.csv
Check that raw/climate_dat_TVSF.zip is unzipped
```{r}
site = fread(paste0(outDir, "UVAFME2018_site.csv"))
clim1983 = fread(paste0(dataDir, "climate_dat_TVSF/climateNAinput_1983_1983-2021MP.csv"))
clim2013 = fread(paste0(dataDir, "climate_dat_TVSF/climateNAinput_2013_2013-2021MP.csv"))
climr45 = fread(paste0(dataDir, "climate_dat_TVSF/climateNAinput_8GCMs_ensemble_ssp245_2022-2100MP.csv"))
climr85 = fread(paste0(dataDir, "climate_dat_TVSF/climateNAinput_8GCMs_ensemble_ssp585_2022-2100MP.csv"))

GCM45 = rbind(clim1983, clim2013, climr45)
GCM85 = rbind(clim1983, clim2013, climr85)

climateGCM = site %>% select(site, latitude, longitude)
GCM45 = select(GCM45, contains(c("Year","id1","Tmin","Tmax","PPT")))
GCM85 = select(GCM85, contains(c("Year","id1","Tmin","Tmax","PPT")))

GCM45 = merge(GCM45, climateGCM, by.x = "id1", by.y = "site")
GCM85 = merge(GCM85, climateGCM, by.x = "id1", by.y = "site")

GCM45 = GCM45[,c(1, 39, 40, 2, 3:38)]
GCM85 = GCM85[,c(1, 39, 40, 2, 3:38)]

cols = c("site" ,"latitude" ,"longitude"  ,"year" ,"tmin_jan" ,"tmin_feb" ,"tmin_mar" ,"tmin_apr" ,"tmin_may" ,"tmin_jun" ,"tmin_jul" ,'tmin_aug' ,"tmin_sep" ,"tmin_oct" ,"tmin_nov" ,"tmin_dec" ,"tmax_jan" ,"tmax_feb" ,"tmax_mar" ,"tmax_apr" ,"tmax_may" ,"tmax_jun" ,"tmax_jul" ,"tmax_aug" ,"tmax_sep" ,"tmax_oct" ,"tmax_nov" ,"tmax_dec" ,"prcp_jan" ,"prcp_feb" ,"prcp_mar" ,"prcp_apr" ,"prcp_may" ,"prcp_jun" ,"prcp_jul" ,"prcp_aug" ,"prcp_sep" ,"prcp_oct" ,"prcp_nov" ,"prcp_dec")
colnames(GCM45) = cols
colnames(GCM85) = cols

GCM45 = GCM45[order(GCM45$site, GCM45$year),]
GCM85 = GCM85[order(GCM85$site, GCM85$year),]
fwrite(GCM45, paste0(outDir, "UVAFME2018_climate_GCM_SSP245.csv"), quote = F, row.names = F)
fwrite(GCM85, paste0(outDir, "UVAFME2018_climate_GCM_SSP585.csv"), quote = F, row.names = F)
```

Building lightningGCM.csv
```{r}
lightning = fread(paste0(outDir, "UVAFME2018_lightning.csv"))
histclim = fread(paste0(outDir, "UVAFME2018_climate.csv"))
GCM45 = fread(paste0(outDir, "UVAFME2018_climate_GCM_SSP245.csv"))
GCM85 = fread(paste0(outDir, "UVAFME2018_climate_GCM_SSP585.csv"))

lightningGCM45 = data.frame(matrix(ncol=16 ,nrow=0, dimnames=list(NULL, c(colnames(lightning)[1:3], "year", colnames(lightning)[4:15]))))
lightningGCM85 = data.frame(matrix(ncol=16 ,nrow=0, dimnames=list(NULL, c(colnames(lightning)[1:3], "year", colnames(lightning)[4:15]))))

histclim = histclim %>% group_by(site) %>% mutate(tave_jan = (tmin_jan+tmax_jan)/2,
                                                  tave_feb = (tmin_feb+tmax_feb)/2,
                                                  tave_mar = (tmin_mar+tmax_mar)/2,
                                                  tave_apr = (tmin_apr+tmax_apr)/2,
                                                  tave_may = (tmin_may+tmax_may)/2,
                                                  tave_jun = (tmin_jun+tmax_jun)/2,
                                                  tave_jul = (tmin_jul+tmax_jul)/2,
                                                  tave_aug = (tmin_aug+tmax_aug)/2,
                                                  tave_sep = (tmin_sep+tmax_sep)/2,
                                                  tave_oct = (tmin_oct+tmax_oct)/2,
                                                  tave_nov = (tmin_nov+tmax_nov)/2,
                                                  tave_dec = (tmin_dec+tmax_dec)/2)

GCM45 = GCM45 %>% group_by(site, year) %>% mutate(tave_jan = (tmin_jan+tmax_jan)/2,
                                                  tave_feb = (tmin_feb+tmax_feb)/2,
                                                  tave_mar = (tmin_mar+tmax_mar)/2,
                                                  tave_apr = (tmin_apr+tmax_apr)/2,
                                                  tave_may = (tmin_may+tmax_may)/2,
                                                  tave_jun = (tmin_jun+tmax_jun)/2,
                                                  tave_jul = (tmin_jul+tmax_jul)/2,
                                                  tave_aug = (tmin_aug+tmax_aug)/2,
                                                  tave_sep = (tmin_sep+tmax_sep)/2,
                                                  tave_oct = (tmin_oct+tmax_oct)/2,
                                                  tave_nov = (tmin_nov+tmax_nov)/2,
                                                  tave_dec = (tmin_dec+tmax_dec)/2)

GCM85 = GCM85 %>% group_by(site, year) %>% mutate(tave_jan = (tmin_jan+tmax_jan)/2,
                                                  tave_feb = (tmin_feb+tmax_feb)/2,
                                                  tave_mar = (tmin_mar+tmax_mar)/2,
                                                  tave_apr = (tmin_apr+tmax_apr)/2,
                                                  tave_may = (tmin_may+tmax_may)/2,
                                                  tave_jun = (tmin_jun+tmax_jun)/2,
                                                  tave_jul = (tmin_jul+tmax_jul)/2,
                                                  tave_aug = (tmin_aug+tmax_aug)/2,
                                                  tave_sep = (tmin_sep+tmax_sep)/2,
                                                  tave_oct = (tmin_oct+tmax_oct)/2,
                                                  tave_nov = (tmin_nov+tmax_nov)/2,
                                                  tave_dec = (tmin_dec+tmax_dec)/2)

#Methods from Foster et al 2022:
# Change in lightning strike frequency was forced according to predictions in
# Veraverbeke et al. (2017). Veraverbeke et al. (2017) predicted a 24% and 59%
# increase in lightning strike frequency for the Northwest Territories and interior
# Alaska, respectively during a 2.84ºC and 2.85ºC increase in temperature, respectively. We thus scaled lightning strike frequency by 20.7% (59/2.85) for each
# degree C increase for interior Alaska and by 8.45% (24/2.84) for each degree C
# increase in the Northwest Territories.


histclim = histclim[order(histclim$site),]
GCM45 = GCM45[order(GCM45$site, GCM45$year),]
GCM85 = GCM85[order(GCM85$site, GCM85$year),]
for (y in 2022:2100) {
  tempdiff = GCM45[GCM45$year == y,41:52] - histclim[,40:51]
  lGCM45 = mapply(`*`, 1+(0.207*tempdiff), lightning[,4:15])
  lightningGCM45 = rbind(lightningGCM45, cbind(lightning[,1:3], rep(y, nrow(lightning)), lGCM45))
  
  tempdiff = GCM85[GCM85$year == y,41:52] - histclim[,40:51]
  lGCM85 = mapply(`*`, 1+(0.207*tempdiff), lightning[,4:15])
  lightningGCM85 = rbind(lightningGCM85, cbind(lightning[,1:3], rep(y, nrow(lightning)), lGCM85))
}

colnames(lightningGCM45) =c(colnames(lightning)[1:3], "year", colnames(lightning)[4:15])
colnames(lightningGCM85) =c(colnames(lightning)[1:3], "year", colnames(lightning)[4:15])

fwrite(lightningGCM45, paste0(outDir, "UVAFME2018_lightning_GCM_SSP245.csv"))
fwrite(lightningGCM85, paste0(outDir, "UVAFME2018_lightning_GCM_SSP585.csv"))

```

Building sitelist, rangelist
```{r}
sitelist = cbind(site$site, 1:nrow(site))
colnames(sitelist) = c("siteID","runID")
sitelist = as.data.frame(sitelist)
sitelist$altitude = NA; sitelist$end = NA
write.csv(sitelist, paste0(outDir, "UVAFME2018_sitelist.csv"), quote = F, row.names = F, na = "")

rangelist  = site %>% select(site, latitude, longitude)
rangelist$ALNUsinu = 1
rangelist$ALNUtenu = 1
rangelist$BETUneoa = 1
rangelist$LARIlari = 0
rangelist$PICEglau = 1
rangelist$PICEmari = 1
rangelist$POPUbals = 1
rangelist$POPUtrem = 1
rangelist$SALIplan = 0
rangelist$SALIscou = 1

write.csv(rangelist, paste0(outDir, "UVAFME2018_rangelist.csv"), quote = F, row.names = F)
```

Building initialization files
strata_init_* are generated from init_strata_summaries.Rmd
```{r}
site = fread(paste0(outDir, "UVAFME2018_site.csv"))
locs = fread(paste0(tempDir, "unit_stratum_date_locs.csv"))
key = fread(paste0(tempDir,"stratum_key.csv"))
init_sp_vol1 = fread(paste0(tempDir,"strata_init_sp_vol1.csv"))
init_dbh_vol1 = fread(paste0(tempDir,"strata_init_dbh_vol1.csv"))
init_sp_vol2 = fread(paste0(tempDir,"strata_init_sp_vol2.csv"))
init_dbh_vol2 = fread(paste0(tempDir,"strata_init_dbh_vol2.csv"))


site = merge(site, locs, by.x = c("longitude","latitude"), by.y = c("x","y"))
init_sp = site %>% dplyr::select(site, STRATUM, UNIT)
init_dbh = site %>% dplyr::select(site, STRATUM, UNIT)
#Unit 3 is Tok (volume 2)

init_sp1 = merge(init_sp[init_sp$UNIT < 3,], init_sp_vol1, by.x = "STRATUM", by.y = "stratum")
init_sp2 = merge(init_sp[init_sp$UNIT == 3,], init_sp_vol2, by.x = "STRATUM", by.y = "stratum")
init_sp = rbind(init_sp1, init_sp2)
init_sp$BA = -999
init_sp = init_sp[,-c(1,3)]
init_sp = init_sp[,c(1,2,13,3:12)]

init_dbh1 = merge(init_dbh[init_dbh$UNIT < 3,], init_dbh_vol1, by.x = "STRATUM", by.y = "stratum")
init_dbh2 = merge(init_dbh[init_dbh$UNIT == 3,], init_dbh_vol2, by.x = "STRATUM", by.y = "stratum")
init_dbh = rbind(init_dbh1, init_dbh2)
init_dbh = init_dbh[,-c(1,3)]


write.csv(init_sp, paste0(outDir, "UVAFME2018_init_spec.csv"), row.names = F, quote = F)
write.csv(init_dbh, paste0(outDir, "UVAFME2018_init_dbh.csv"), row.names = F, quote = F)

#Finally, edit site file to saturate dwarf black spruce sites:
site = as.data.frame(site)
site[site$STRATUM == 20,]$hum_init = 200
site[site$STRATUM == 20,]$a_sat = max(site[site$STRATUM == 20,]$a_sat, 0.45)
site[site$STRATUM == 20,]$o_sat = max(site[site$STRATUM == 20,]$o_sat, 0.45)
site[site$STRATUM == 20,]$a_fc = max(site[site$STRATUM == 20,]$a_fc, 0.3)
site[site$STRATUM == 20,]$o_fc = max(site[site$STRATUM == 20,]$o_fc, 0.3)

site[site$STRATUM != 20,]$a_sat = min(site[site$STRATUM == 20,]$a_sat, 0.35)
site[site$STRATUM != 20,]$o_sat = min(site[site$STRATUM == 20,]$o_sat, 0.35)
site[site$STRATUM != 20,]$a_fc = min(site[site$STRATUM == 20,]$a_fc, 0.2)
site[site$STRATUM != 20,]$o_fc = min(site[site$STRATUM == 20,]$o_fc, 0.2)
site[site$STRATUM != 20,]$a_pwp = min(site[site$STRATUM == 20,]$a_pwp, 0.06)
site[site$STRATUM != 20,]$o_pwp = min(site[site$STRATUM == 20,]$o_pwp, 0.06)

site$unit = site$unit.x
site = site %>% dplyr::select(site,latitude,longitude,name,region,elevation,slope,aspect,a_sat,a_fc,a_pwp,o_sat,o_fc,o_pwp,a_bd,o_bd,itxt,hum_init,A_depth,wprob,flow,row,col,ind,management,sel_cutting,planting,viability,rotation_time,dbh_thresh,thinning,year_management,thin_perc,shearblading,pruning,unit,init_year)

# site$prescribed_burn = 0 # we could change this if we knew a site experienced disturbance after it was last inventoried

write.csv(site, paste0(outDir, "UVAFME2018_site.csv"), row.names = F, quote = F)
```

Create runtimes by hand... there are only 6
Also,  current specieslist and litterpars were copied from other directories